---
title: "GenRt"
author: "Michael Thane"
date: "14 9 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)

```

# Generative Art Using R
## Create the data set
There is a great potential for creating digital art by using R’s ggplot2 library and create visualizations that look like real art works. Mainly those approaches use data sets which are based on mathematical formulas and can be manipulated as desired. 
My approach of creating digital art using R is quite similar. First I created a data set that is based on three random variables “X”, “Y” and “Z” and one grouping variable “Group”. These distributions are based on a normal distribution with a given mean and standard deviation.


```{r create_data}

generate_data <- function(N,ngroup,xmean,xvar,ymean,yvar,zmean,zvar){
   DAT=data.frame()

  names=paste("G_",seq(1,ngroup),sep="")
  DAT=data.frame()
  for(i in seq(1:ngroup)){
      data=data.frame( matrix(0, ngroup , 4))
      data[,1]=sample(names, nrow(data))
      data[,2]=sample( c(rnorm(N,mean = xmean,sd = xvar),c(1:ngroup)) ,nrow(data))
      data[,3]=sample( c(rnorm(N,mean=ymean,sd = yvar),c(1:ngroup)) ,nrow(data))
      data[,4]=sample( c(rnorm(N,mean=zmean,sd = zvar),c(1:ngroup)) ,nrow(data))
      DAT=rbind(DAT,data)
  }
  colnames(DAT)=c("Group","X","Y","Z")
  DAT
}
gendata <- generate_data(1050,5,1,2,3,4,5,6)
head(gendata)
```

## Create the plot
Using this data one can now plot an “art work”. I was trying to find attributes that would make the art works look quite different, but that can later also been used to find out which kind of art is preferred by the user. The attributes are the following:

1. N (Number of samples)
2. ngroups (Number of different groups)
3. xmean, ymean, zmean (means of the distributions)
4. xsd, ysd, zsd (standard deviations of the distributions)


5. geom (what kind of geometric is used in the art work)
6. alpha (opacity value)
7. polar (using polar coordinate system)
8. size (size of the geometric objects)
9. ncolor (number of different colors)
11. colorscale (which color scale is being used)

To find these attributes I was playing around with the outcome a bit, and it seemed that these attributes create various different visualizations. Some of these visualizations looked rather boring to me and some I enjoyed looking at. These visualizations will be used for the recommendation in the next step.



```{r generate_plot}

generate_plot <- function(DAT,colorscale="Set1",size=5,alpha=0.5,geom=1,polar=F){

  p <- ggplot() +
    
    scale_color_brewer(palette = colorscale) +
    scale_fill_brewer(palette = colorscale) +
    #geom_col()+
    #theme_bw()# +
    theme(
      line = element_blank(),
      text = element_blank(),
      title = element_blank(),
      legend.position = "none",
      panel.border = element_blank(),
      panel.background = element_blank()
    )
  
  
  if (geom == 1) {
    p <- p + geom_col(
      aes(
        x = X,
        y = Y,
        color = Group,
        group = Group
      ),
      size = size,
      alpha = alpha,
      data = DAT
    )
  }
  if(geom==2){
      p <- p+geom_tile( aes(x=X,
                            y=Y,
                            height = Z,

                            color=Group,
                            group=Group,
                            width=size
      ), size=size,
      alpha=alpha,data = DAT)
  }
  if(geom==3){
     p <- p+geom_boxplot( aes(x=X,
                              y=Y,

                              color=Group,
                              group=Group
     ), size=size,
     alpha=alpha,data = DAT)
  }
  if(geom==4){
    p <- p+geom_violin( aes(x=Group,
                            y=Y,

                            color=Group
    ),  size=size,
    alpha=alpha,data = DAT)
  }

  if(geom==5){
      p <- p+geom_area( aes(x=X,
                            y = Y,


                            color=Group,
                            group=Group
      ), size=size,alpha=alpha,data = DAT)
  }

  if(geom==6){
      p <- p+geom_point( aes(x=X,
                             y=Y,

                             color=Group
      ),size=size,
      alpha=alpha,data = DAT)
  }

  if(geom==7){
      p <- p+geom_line( aes(x=X,
                            y=Y,
                            z=Z,

                            color=Group,
                            group=Group
      ), size=size,
      alpha=alpha,data = DAT)
  }
  if(geom==8){
      p <- p+geom_spoke( aes(x=X,y=Y,angle=Z,color=Group
      ),
      alpha=alpha,radius=size,size=size,data = DAT)
  }

  
  
  if(polar==T){
      p <- p+coord_polar()
  }
  p
    
}
generate_plot(gendata)
```

Below the same function is called, but this time with different parameters.

```{r generate_plot2}
gendata
generate_plot(gendata,colorscale = "Set2",size = 15,geom = 9,polar = T)

```


## Create various configurations
For creating various different visualizations I created a function that will create random configurations of the attributes.

```{r generate_configurations}

generate_config <- function(NPOP){
  data.frame(
    list(
      id = seq(1, NPOP),
      geom = sample(1:8, NPOP, replace = T),
      ngroups = sample(2:30, NPOP, replace = T),
      N = sample(150:1500, NPOP, replace = T),
      xmean = sample(1:5, NPOP, replace = T),
      ymean = sample(1:5, NPOP, replace = T),
      zmean = sample(1:5, NPOP, replace = T),
      xvar = sample(1:50, NPOP, replace = T),
      yvar = sample(1:50, NPOP, replace = T),
      zvar = sample(1:50, NPOP, replace = T),
      alpha = runif(NPOP, 0, 1),
      polar = sample(c(T, F), NPOP, replace = T),
      size = sample(seq(1, 100, 1), NPOP, replace = T),
      ncolor = sample(2:8, NPOP, replace = T),
      colorscale = sample(
        c(
          "Set1",
          "Set2",
          "Set3",
          "Pastel1",
          "Pastel2",
          "Paired",
          "Dark2",
          "Accent",
          "Blues",
          "Greys",
          "BuGn",
          "Reds",
          "Oranges",
          "Greens"
        ),
        NPOP,
        replace = T
      ),
      score = rep(NA, NPOP),
      pred_score = rep(NA, NPOP),
      rated = rep(F, NPOP)
    )
  )
}
generate_config(10)

```
